Drivers of Phytoplankton Community Variability in the Cariaco Basin, Venezuela

### 2024-09-26 main.tex
Updated to AGU Template

@@

            \item sediment traps (?)

>>>>

            Understanding the link between ocean surface and the sinking flux of particulate carbon in the Cariaco Basin.
                a large (\∼160 km long, 70 km wide) and deep (∼1,400 m) basin, located on the Venezuelan continental shelf
                bound to the north by a sill at a mean depth of about 100 m
                productive area (\~400 gC/m²y)
                Primary production and vertical particulate organic matter fluxes are higher than BATS and HOT locations → anoxic bottom waters!

@@
